\section{eTrice Java Projects}

There are two flavors of \eTrice{} Java projects. The first one uses the Eclipse JDT build and the
second one uses Maven to build and deploy an \eTrice{} application.

The kind of build can be selected in the "Empty eTrice Java project" wizard.

\subsection{Eclipse JDT Build}

If this kind of build is chosen the \eTrice{} new project wizard requires the \texttt{org.eclipse.etrice.runtime.java}
project in the workspace and adds a dependency to it.

If the project uses other \eTrice{} projects (e.g. the \texttt{org.eclipse.etrice.modellib.java})
they have to be added to the Java build path as well.

The \eTrice{} new project wizard creates the following files for the JDT build
\begin{itemize}
\item a ROOM model file with exemplary classes
\item a simple physical model
\item a model mapping the logical entities of the ROOM model to the physical entities
\item a launch configuration that invokes the \eTrice{} Java code generator for the new models
\item a launch configuration that launches the main method of the generated code
\end{itemize}

If "build automatically" is chosen the newly created model can be generated and launched with just two clicks.

\subsection{Maven Build}

The Maven integration of eTrice requires the m2eclipse plug-in installed. The dependencies are then managed
by the Maven pom.xml but the e2m builder maps them as JDT visible dependencies to the project class path.

As a preparation the \texttt{org.eclipse.etrice.runtime.java} should be imported to the workspace
using the \eTrice{} new wizard. Then execute the \texttt{install\_org.eclipse.etrice.runtime.java.launch}
Maven launch configuration (or execute \texttt{mvn install} from the command line). This installs the \eTrice{}
Java runtime as a Maven component to the local repository.

Then perform similar steps for the \texttt{org.eclipse.etrice.modellib.java}.

The \eTrice{} new project wizard creates the following files for the Maven build
\begin{itemize}
\item a ROOM model file with exemplary classes
\item a simple physical model
\item a model mapping the logical entities of the ROOM model to the physical entities
\item a launch configuration that invokes the \eTrice{} Java code generator for the new models
\item a launch configuration that builds and deploys the generated application
\item a launch configuration that launches the deployed jar file
\item a launch configuration that launches the main method of the generated code (for convenience or
if the generated code should be launched in debug mode)
\end{itemize}

After the new project is created the m2e builder creates the dependencies in the project class path.
Therefore also JDT can compile and launch the application.

When the packaging of the project succeeded two jar files have been created in the \texttt{target} folder.
The larger one with "jar-with-dependencies" in its name also contains the referenced Maven components. It can be
launched using the \texttt{runjar\_*} launch configuration.
